Local simple connectedness of boundaries of hyperbolic groups

### 2020-04-06 paper.tex
Minor changes up to lemma 5.3

\begin{proposition}\label{prop:i_in_dimension_2}
  There are constants $n_0$ and $L$ such that for each $n\geq n_0$ there is map
  $i^n_{n+1}\from\Skel_2 K_n \to \Skel_2 K_{n+1}$ such that the
  following conditions hold.
  \begin{enumerate}
    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
      $\sd_L\Skel_2 K_n$,
    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 2\delta+1$,
      and
  \end{enumerate}
\end{proposition}

\begin{proof} 
  Let $n_0$ be as in Proposition~\ref{prop:i_in_dimension_1} and for $n \geq
  n_0$ let $i^n_{n+1} \from \Skel_1 K_n \to \Skel_1 K_{n+1}$ be the maps given
  by that proposition, so there exists $M$ such that $i^n_{n+1}$ is a
  simplicial map on $\sd^M\Skel_1 K_n$, and this map is a simplicial
  approximation to a map that factors through $p^\infty_{n+1} \from \boundary G
  \to K_{n+1}$.

  Then $\S_M$ gives numbers $L$ and $n_0' \geq n_0$ such that for $n \geq
  n_0'$, for any 2-simplex $\sigma$ of $K_n$, $i^n_{n+1}\restricted\boundary
  \sigma$ admits an extension to $\sigma$ that is affine on $\sd^L\sigma$.
  Gluing these extensions together extends $i^n_{n+1}$ to a map $\sd^2 K_n \to
  \sd_2 K_{n+1}$ with the required properties.
\end{proof}

\begin{definition}
  With the notation of Proposition~\ref{prop:i_in_dimension_2}, for $n \geq m
  \geq n_0$ let $i^n_m \from \Skel_2 K_m \to \Skel_2 K_n$ be the composition
  $i^{n-1}_n \composed \dotsb \composed i^m_{m+1} \from \Skel_2 K_m \to 
  \Skel_2 K_n$.  This map is affine on a degree $L^{n-m}$ subdivision of 
  $\Skel_2 K_m$.
\end{definition}

>>>>

\begin{proposition}\label{prop:i_in_dimension_2}
  There are constants $n_0$ and $L$ such that for each $n\geq n_0$ there is map
  $i^n_{n+1}\from\Skel_2 K_n \to \Skel_2 K_{n+1}$ with the following properties.
  \begin{enumerate}
    \item For each $n$, $i^n_{n+1}$ is an affine map on the subdivision
      $\sd_L\Skel_2 K_n$.
    \item For any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 2\delta+1$.
  \end{enumerate}
\end{proposition}

\begin{proof} 
  Let $n_0$ be as in Proposition~\ref{prop:i_in_dimension_1} and for $n \geq
  n_0$ let $i^n_{n+1} \from \Skel_1 K_n \to \Skel_1 K_{n+1}$ be the maps given
  by that proposition, so there exists $M$ such that $i^n_{n+1}$ is a
  simplicial map on $\sd^L\Skel_1 K_n$, and this map is a simplicial
  approximation to a map that factors through $p^\infty_{n+1} \from \boundary G
  \to K_{n+1}$.

  Then $\S_L$ gives numbers $L'$ and $n_0' \geq n_0$ such that for $n \geq
  n_0'$, for any 2-simplex $\sigma$ of $K_n$, $i^n_{n+1}\restricted{\boundary
  \sigma}$ admits an extension to $\sigma$ that is affine on $\sd^{L'}\sigma$.
  Gluing these extensions together extends $i^n_{n+1}$ to a map $\Skel_2 K_n \to
  \Skel_2 K_{n+1}$ with the required properties.
\end{proof}

\begin{definition}
  With the notation of Proposition~\ref{prop:i_in_dimension_2}, for $n \geq m
  \geq n_0$ let $i^m_n \from \Skel_2 K_m \to \Skel_2 K_n$ be the composition
  $i^{n-1}_n \composed \dotsb \composed i^m_{m+1} \from \Skel_2 K_m \to 
  \Skel_2 K_n$.  This map is affine on the degree $L^{n-m}$ barycentric
  subdivision of $\Skel_2 K_m$.
\end{definition}
